Lyman-alpha spectra from rotating outflows

### 2017-11-08 paper/paper.tex
adding reference, missing text
missing kulas, doppler explanation and more conclusions

In order to compare the line created with the radiative transfer process that 
involves the rotation (RT) and the line with only outflows that is Doppler 
shifted (DS), we calculate three main characteristics for each spectrum. We 
measure the line's mean velocity, standard deviation and skewness for both 
RT's and DS's approaches. We plot the results for each value in Figures 
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness}, 
respectively for the same \tauh as Figure \ref{fig:doppler_shift}.

@@

\subsection{Theoretical Insights}
Talk about radiative transfer...

Regarding de Doppler shift... Then, the quality and accuracy of 
the spectrum, obtained by a Doppler shift, increases with the optical depth \tauh. 
This is because the more \tauh, the more anisotropic is the photons' distribution 
at the galaxy's border.

The introduction of rotation in the model implies that it will only affect 
galaxies with its viewing angle...

@@

Kulas...

MUSE...

@@

@@

In this appendix we show Figures \ref{fig:varying_rotation} and \ref{fig:varying_outflow} with more combinations of \vrot and \vout.

>>>>

In order to compare the line created with the radiative transfer process that 
involves the rotation (RT) and the line with only outflows that is Doppler 
shifted (DS), we calculate three main characteristics for each spectrum. We 
measure the line's mean velocity, standard deviation and skewness for both 
RT's and DS's approaches. We plot the results for each value in Figures 
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness}, 
respectively for $\tauh = 10^7$. We highlight that these 3 plots increase
their fit tendency with a higher optical depth. The reasons why will be 
discussed in section \ref{sec:discussion}.

@@

\subsection{Theoretical Insights}
\color{red}
Why Doppler Shift works. Talk about radiative transfer...
\color{black}

A first approach to an analytical expression that returns the \lya spectrum 
from a rotating galaxy is presented by \cite{Garavito14}. This derivation is 
based on the assumption that the distribution of photons' propagation directions
at the edge of the galaxy is anisotropic and depends of \tauh only. So this 
approximation becomes more accurate with higher optical depth and it is also the 
reason why the Doppler Shift technique to induce rotational effects to an outflow
\lya spectrum works.

On the other hand, regarding the parameters \vrot, \vout, and $\theta$ for
which this model would work, we have the following. The effect of the outflows 
velocity is much more sensitive on the spectrum than the rotational one; meaning 
that for a high \vout, the \vrot value would have to be equal or greater in order 
to be able to glimpse the shift in frequency that rotation induces. Regarding $\theta$, 
the introduction of rotation in the model implies that it will only affect galaxies 
with its viewing angle $\theta \neq 90^\circ$. This can be observed in the cartesian 
components of the velocity of the atoms (Eq. \ref{eq:vx}, \ref{eq:vy}, \ref{eq:vz})
where the only velocity factor affecting $v_z$ is the outflows one.

@@

We find three different approaches how this model can have observational
implications. Firstly, as the resolution of astronomical instruments is 
increasing, new images from LAEs can be spatially resolved in a way that 
rotation velocities of the galaxy can be determined. New spectrographs like 
MUSE should help obtain kinematic information from LAEs by using our model.  
As for now, previous works in the literatures have already found useful data
to support this idea. Fig 7 of Prescott et al. \cite{Prescott14} shows the
presence of Doppler shift and \cite{Herenz2016} creates 2D line of sight 
velocity maps of several LARS (Lyman Alpha Reference Sample) galaxies.

Another application of this new model to the current interpretation of \lya
spectra, is that the central ($V=0$) emission of the spectra seen in the 
\lya line, is a consequence of the viewing angle of the galaxy and can be 
controlled by it. Several authors have suggested that this central emission 
is caused by radiation that escapes the galaxy without scattering. So we 
present an alternative that solves this issue. In addition, the effect of
outflows velocities \vrot in current models can modify the asymmetry of peaks
present in the \lya line. However the intensity of the valley and the width 
of the line were not easily reproduced. In this work we provide a tool to
provide these effects with values of \vout and \vrot that do not exceed the
typical LAEs' numbers found in the literature.

\color{red}
Kulas...
\color{black}
Finally, we present a reconstruction of a selected \lya spectrum presented
by \cite{Kulas12} and reproduced with the permission of the author. We create
a fit of the \lya line and predict its kinematic properties.

@@

In this paper we create, for the first time, a computational model for LAEs 
that emulate the kinematic effects of galaxy rotation and outflows in the \lya
spectral line.

\color{red}
Complete conclusions...
\color{black}

@@

In this appendix we show more \lya spectra in the Figures 
\ref{fig:varying_rotation} and \ref{fig:varying_outflow} 
with more combinations of \vrot and \vout.
